<<<<<<< HEAD
---
title: "Word Cloud"
author: "Abhinav Yedla"
date: "October 9, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Complete Set of Words

This canvas include `min(Top frequency 250 words, total words with atleast 10 frequency)` from complete set.For detials on how data is collected or for API access see <https://github.com/AbhinavYedla/gautocompleter>.

## Word canvas

```{r pressure, echo=FALSE}
suppressMessages(library(tm))
suppressMessages(library(SnowballC))
suppressMessages(library(wordcloud))

data <-
  read.delim("GoogleAutoComplete_Tidy_2_Countries.txt", sep = "\t")

corpus <- Corpus(VectorSource(data[, c(-1,-2,-3,-4)]))
corpus <- tm_map(corpus, PlainTextDocument)
corpus <- tm_map(corpus, removePunctuation)
corpus <-
  tm_map(corpus,
         removeWords,
         c('the', 'this', 'No Value', stopwords('english')))

wordcloud(corpus, max.words = 300, random.order = FALSE,colors = rainbow(n = 100),min.freq = 10)
```
=======
---
title: "Word Cloud Universe"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
>>>>>>> 146238c6ca180b86f74fe90b6ce5640c6a36aa06
